---
title: "pa_1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
dur_hablo_stressed = 466.524
dur_hablo_unstressed = 431.445 
dur_o_stressed = 206.571 
dur_o_unstressed = 112.002 
int_o_stressed = 89.12363657574684 
int_o_unstressed = 81.35578152786863 
f0_o_stressed = 213.50404026286904 
f0_o_unstressed = 79.6648661980173
a = -35.079
b = 94.569
c = 7.767855
d = 133.8392

```



# Calculations


a The difference in ms between “hablo” and “habló” 
```{r} 
dur_hablo_unstressed - dur_hablo_stressed
```

b The difference in ms between the stressed and unstressed [o]

```{r} 
dur_o_stressed - dur_o_unstressed 
```

c The difference in intensity between the stressed and unstressed [o]
```{r} 
int_o_stressed - int_o_unstressed
```
d The difference in F0 between the stressed and unstressed [o]
```{r}
f0_o_stressed - f0_o_unstressed
```


# Observations


The difference in milliseconds between “hablo” and “habló” is of `r a` Ms in the same way, we can also observe how the stressed vowel [o] has also a longer duration of `r b`Ms. Results show that the given speaker produces longer duration times when pronouncing stressed words.  

Regarding the intensity and the F0 distinctions, we find no surprises here, being the difference in intensity between the stressed and unstressed of `r c` dB, and between F0 stressed and unstressed `r d` Hz. 

